Macro Impacts

### 2016-08-19 Macro Impacts Revised.tex
update

\section{Fourier Series}
We take the Fourier series in time along the direction of the pulse
u =\f{1}{2\pi L} \sum_{k = 0}^{N} U(k) e^{-2\pi \I \f{L k}{N}(x -v_p t)}
\partial_t u = \f{\I v_p}{(2\pi L)^2} \sum_{k = 0}^{N} k U(k) e^{-2\pi \I \f{L k}{N}(x -v_p t)}\,.
E &= A_{\te{ray}}\rho \int_0^L\diff x\abs{\partial_t u}^2\,,\\
&= A_{\te{ray}}\rho \int_0^L\diff x\f{v_p^2}{(2\pi L)^2} \sum_{k,k' = 0}^{N} k k' U(k)\bar U(k') e^{-2\pi \I \f{L (k-k')}{N}(x -v_p t)}\,,\\
&= A_{\te{ray}}\rho \f{v_p^2}{(2\pi L)^2} \sum_{k,k' = 0}^{N} k k' U(k)\bar U(k') \int_0^L\diff x e^{-2\pi \I \f{L (k-k')}{N}(x -v_p t)}\,,\\
&= A_{\te{ray}}\rho \f{v_p^2}{(2\pi L)^2} \sum_{k,k' = 0}^{N} k k' U(k)\bar U(k') 2\pi L\delta_{k k'}e^{2\pi \I \f{L (k-k')}{N}(v_p t)}\,,\\
&= A_{\te{ray}}\rho \f{v_p^2}{2\pi L} \sum_{k= 0}^{N} k^2 \abs{U(k)}^2\,.
E_k =  A_{\te{ray}}\rho \f{v_p^2}{2\pi L} k^2 \abs{U(k)}^2\,.
What is $E_k$? Using the general cylindrically symmetric source from before, we know $E_k= C_1 \f{k^2}{(2\pi L)^2}$. Solving for $\abs{U}$, we have
\abs{U(k)} = \sqrt{\f{2\pi L}{v_p^2 A_{\te{ray}}\rho}\f{E_k}{ k^2}}
In our case, we have
\abs{U(k)} = \sqrt{\f{C_1}{2\pi L v_p^2 A_{\te{ray}}\rho}}\,.
This is just a constant, so $U(k)$ is a pure phase, which comes out of the sum, so
\abs{u} =\f{1}{2\pi L}\sqrt{\f{C_1}{2\pi L v_p^2 A_{\te{ray}}\rho}} \sum_{k = 0}^{N} \cos\p{2\pi\f{L k}{N}(x -v_p t)}
Hm, something's fishy... What about this:

@@

\section{Double Thought Out}
Thanks to Josh for a very useful conversation in helping to deduce what follows:
A key problem we are encountering is what follows. Suppose we shoot out a large number of rays that uniformly hit the surface of the sphere. If we have $N$ rays in a pixel, and then halve the area of the pixel, we will have $N/2$ rays in the pixel. This, in turn, reduces the energy in the pixel, and if not accounted for properly, the measured displacement. If, however, when increase the number of pixels, we also multiply the energy in each pixel by the number of pixels, then assuming a uniform distribution of rays, the average displacement across pixels does not change as the number of pixels increases.
Thus, suppose we have $M$ rays and $N$ pixels. Let $M_j$ be the number of rays incident on pixel $j$. Let $E_k^{ij}$ be the energy of the $i$th ray incident on the $j$th pixel. We then calculate
E_k^j =N\sum_{i=1}^{M_j}E_k^{ij}\,.
We now calculate the displacement, where $C_2^{ij} = v_p \f{T^{ij}}{Q^{ij}}$.
\td{E_k^{j}}{k}{} = N\sum_{i = 1}^{M_j}2 C_1^{ij} k'e^{-C_2^{ij} k}\,.
The integral would be impossible without an approximation
\sqrt{\td{E_k^{j}}{k}{}} & = \sqrt{N\sum_{i = 1}^{M_j}2 C_1^{ij} k'e^{-C_2^{ij} k}}\,,\\
& \leq \sqrt{N\p{\sum_{i = 1}^{M_j}\sqrt{2 C_1^{ij} k'e^{-C_2^{ij} k}}}^2}\,,\\
&=\sqrt{N}\sum_{i = 1}^{M_j}2 C_1^{ij} \sqrt{k'}e^{-C_2^{ij}\f{k}{2}}\,.
u_k^j&\leq\f{\sqrt{N}}{2\pi kv_p\sqrt{\rho}}\sum_{i}^{M_j}\f{\sqrt{E_k^{ij}}}{C_2^{ij}}\p{\sqrt{ \f{2\pi}{C_2^{ij}}}\te{Erf}\ps{\sqrt{\f{k}{2}C_2^{ij}}} -2\sqrt{k} e^{-\f{k }{2}C_2^{ij}}}\,.

>>>>

\section{Directed Ray}
This time, we assume the oscillation is just in the $x$ direction.

@@
